\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}
	\par Making this \textbf{game} was a very \textbf{gratifying} and \textbf{fulfilling} experience. I succeeded to \textbf{implement} all of the \textbf{mechanics} and \textbf{features} of the original game's \textbf{medium difficulty} gameplay. The application can be \textbf{downloaded} and \textbf{played} on \textbf{Android }mobile devices. 
	\par The \textbf{user} can \textbf{pause, resume, save} and \textbf{quit} the game with no negative impact on the \textbf{time progression} and the \textbf{permanent death} feature. The \textbf{environment} has all the original \textbf{locations} and \textbf{resources}. \textbf{Sleeping, crafting, travel, traps} and \textbf{hunting} were also fully implemented. All the \textbf{inventory items} can be manipulated and used in the intended ways. \textbf{Exploration} and \textbf{resource gathering} have similar, if not identical chance \textbf{values}. 
	\par The \textbf{graphical interface} has \textbf{bright colours} and \textbf{beautiful backgrounds}. The \textbf{screen structure} is similar, but the \textbf{design} was tweaked to my liking. I did not, however, manage to implement a \textbf{sound} system.
	\par I chose to make the \textbf{game} in \textbf{Python} because I have done this before and I was \textbf{comfortable} with it. I am glad I took the time to make a lot of the \textbf{GUI} elements from \textbf{scratch} and learn about \textbf{integration}, but I will not do this again. I cherish the \textbf{knowledge}, but I have gained enough \textbf{confidence} to use \textbf{game engines} from now on.
	\par In \textbf{conclusion}, all of the primary \textbf{objectives} of the \textbf{project} have been \textbf{achieved}.
\newpage